CS6110: Software Verification Final Project: Formal Verification of Rust Programs with Creusot

### 2023-05-05 paper.tex
Cleanup spaces at the end of lines, add start of section on verifying

\begin{document}

@@

\section{Overview of Creusot}

@@

@@

\printbibliography

>>>>

\pagenumbering{gobble}
\begin{document}

@@

\clearpage
\pagenumbering{arabic}
\section{Overview of Creusot}

@@

Consider the following Rust function:

\begin{verbatim}
#[requires(lo < hi)]
#[ensures(^lo < ^hi)]
fn palindrome_range(s: &[u8], lo: &mut usize, hi: &mut usize) {
    #[invariant(*lo < *hi)]
    #[invariant(*lo >= 0)]
    #[invariant(*hi < (s.deep_model()).len())]
    while *lo > 0 && *hi < s.len() - 1 && s[*lo - 1] == s[*hi + 1] {
        lo = lo - 1;
        hi = hi + 1;
    }
}
\end{verbatim}

This function takes a string, and and two integers \texttt{lo} and \texttt{hi} as mutable references.
It walks the string in opposite directions as long as \texttt{lo} and \texttt{hi} index into the same letter: in short, this walks palindromes inside of strings.

We have added some pre- and post-conditions to the function, namely that---as long as \texttt{lo} is less than \texttt{hi} at the beginning---their \emph{final values} will likewise be ordered.
We also need to specify some invariants on the \texttt{while} loop.

@@

\clearpage
\printbibliography
